Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-03-01 paper/main.tex
edits through end of discussion

We developed a computational framework that uses short multiple-choice quizzes
to gain nuanced insights into what learners know and how their knowledge
changes with training. First, we show that our approach can automatically match
the conceptual knowledge probed by individual quiz questions to the corresponding
moments in lecture videos when those concepts were presented
(Fig.~\ref{fig:question-correlations}). Next, we demonstrate how we can
estimate moment-by-moment ``knowledge traces'' that reflect the degree of knowledge
participants have about each video's time-varying content, and capture temporally
specific increases in knowledge after viewing each lecture (Fig.~\ref{fig:knowledge-timeseries}).
 We also show that these knowledge estimates can generalize to held-out questions
(Fig.~\ref{fig:predictions}). Finally, we use our framework to construct visual
maps that provide snapshot estimates of how much participants know about any
concept within the scope of our text embedding model, and how much their
knowledge changes with training (Fig.~\ref{fig:knowledge-maps}).

Over the past several years, the global pandemic has forced many educators to
teach remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
in world circumstances is happening alongside (and perhaps accelerating)
geometric growth in the availability of high quality online courses on
platforms such as Khan Academy~\citep{Khan04}, Coursera~\citep{Youn12},
EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}. Continued expansion of the
global internet backbone and improvements in computing hardware have also
facilitated improvements in video streaming, enabling videos to be easily
shared and viewed by large segments of the world's population. This
exciting time for online course instruction provides an opportunity to
re-evaluate how we, as a global community, educate ourselves and each other.
For example, we can ask: what makes an effective course or training program?
Which aspects of teaching might be optimized and/or augmented by automated tools? How and why do
learning needs and goals vary across people? How might we lower barriers to
achieving a high-quality education?

>>>>

We developed a computational framework that uses short multiple-choice quizzes
to gain nuanced insights into what learners know and how their knowledge
changes with training. First, we show that our approach can automatically match
the conceptual knowledge probed by individual quiz questions to the corresponding
moments in lecture videos when those concepts were presented
(Fig.~\ref{fig:question-correlations}). Next, we demonstrate how we can
estimate moment-by-moment ``knowledge traces'' that reflect the degree of knowledge
participants have about each video's time-varying content, and capture temporally
specific increases in knowledge after viewing each lecture (Fig.~\ref{fig:knowledge-timeseries}).
 We also show that these knowledge estimates can generalize to held-out questions
(Fig.~\ref{fig:predictions}). Finally, we use our framework to construct visual
maps that provide snapshot estimates of how much participants know about any
concept within the scope of our text embedding model, and how much their
knowledge of those concepts changes with training (Fig.~\ref{fig:knowledge-maps}).

Over the past several years, the global pandemic has forced many educators to
suddenly adapt to teaching remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
in world circumstances is happening alongside (and perhaps accelerating)
geometric growth in the availability of high-quality online courses from
platforms such as Khan Academy~\citep{Khan04}, Coursera~\citep{Youn12},
EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}. Continued expansion of the
global internet backbone and improvements in computing hardware have also
facilitated improvements in video streaming, enabling videos to be easily
shared and viewed by increasingly large segments of the world's population. This
exciting time for online course instruction provides an opportunity to
re-evaluate how we, as a global community, educate ourselves and each other.
For example, we can ask: what defines an effective course or training program?
Which aspects of teaching might be optimized and/or augmented by automated tools? How and why do
learning needs and goals vary across people? How might we lower barriers of access
to a high-quality education?
